---
title: "Music Insights"
author: "Olivia Abbott"
output: html_notebook
---

Tidyverse handles data importing and wrangling:

```{r}
install.packages("tidyverse")
library("tidyverse")
```

When importing data use relative paths instead of absolute paths. Use paths reletive to the directory this file is in.

```{r}
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

nrow(survey)
nrow(preferences)
```

Cleaning data column names so that they have a consistant format for the survey table:

```{r}
colnames(survey)
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "psuedonym_generator"
colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey) == "Sex"] <- "sex"
colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "facorite_song_link"

?strsplit
```

Cleaning data column names so that they have a consistant format for the preferences table:

```{r}

```


Tidy data:
  We want to split our two tables into 4 tables:
  1. Person
  2. Favorite Song
  3. Song Ratings
  4. Musical Talents
  

  
  
  
  
  
  
  
  
  