---
title: "Music Insights"
author: "Olivia Abbott"
output:
  html_document:
    df_print: paged
---

Tidyverse handles data importing and wrangling:

We also need to load the librarys dplyr and tidyr:

```{r}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name)
  library(library_name, character.only=TRUE)
}

include("tidyverse")

#install.packages("tidyverse")
#library("tidyverse")
#library("dplyr")
#library("tidyr")
```

When importing data use relative paths instead of absolute paths. Use paths reletive to the directory this file is in.

```{r}
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")

nrow(survey)
nrow(preferences)
```
Data Cleaning for survey:

Cleaning data column names so that they have a consistant format for the survey table:

```{r}
#rename_column <- function(data_frame, column_name, new_name){
#  colnames(data_frame)[colnames(data_frame) == column_name] <- new_name
#  } 
# this function won't change anything because we pass the dataframe by value not by reference
# in R pass by reference is not supported

colnames(survey)[colnames(survey) == "Timestamp"] <- "time_submitted"
colnames(survey)[colnames(survey) == "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "psuedonym_generator"
colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey) == "Sex"] <- "sex"
colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
colnames(survey)
```

Tidy data:
  We want to split our two tables into 4 tables:
  1. Person
  2. Favorite Song
  3. Song Ratings
  4. Musical Talents


To create the person data frame:

```{r}
person <- tibble(time_submitted = survey$time_submitted, pseudonym_generator = survey$psuedonym_generator, pseudonym = survey$pseudonym, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, year_born = survey$year_born)
```

To create the favarite song data frame:

```{r}
favorite_song <- tibble(pseudonym = survey$pseudonym, song = survey$favorite_song, artist = survey$favorite_song_artist, link = survey$favorite_song_link)
```

Cleaning the date data so that it is formatted to the POSIXlt format:

```{r}
library('readr')
?parse_datetime

person$time_submitted <- as.POSIXlt(parse_datetime(person$time_submitted, format = "%m/%d/%y %H:%M"))
```

Cleaning data so that categorical data is represented as factors:
(only use as.factor on categorical data)

```{r}
person$academic_level <- as.factor(person$academic_level)
levels(person$academic_level)

person$academic_major <- as.factor(person$academic_major)
levels(person$academic_major)
# there is an issue with this one since there are different capilalizations of computer information systema
# we need to change the levels so that they are the same category
# change computer information system value
# eliminate other levels so that there is only one computer information systems value
levels(person$academic_major)[levels(person$academic_major) == "Computer information systems"] <-  "Computer Information Systems"
# eliminate other levels so that there is only one computer information systems value
levels(person$academic_major)

```
Data cleaning for preferences:

Cleaning data column names so that they have a consistant format for the preferences table:

```{r}
colnames(preferences)[colnames(preferences) == "Timestamp"] <- "time_submitted"
colnames(preferences)[colnames(preferences) == "What was your pseudonym?"] <- "pseudonym"
```

Create Ratings table from the preferences table to make data tidy:

```{r}
preferences <-  gather(preferences, key = "artist_song", value = "rating", -time_submitted, -pseudonym)
ratings <- tibble(time_submitted = preferences$time_submitted, pseudonym = preferences$pseudonym, artist_song = preferences$artist_song, rating = preferences$rating)
```

Cleaning the date data so that it is formatted to the POSIXlt format:

```{r}
ratings$time_submitted <- as.POSIXlt(parse_datetime(ratings$time_submitted, format = "%m/%d/%y %H:%M"))
```

Cleaning data so that categorical data is represented as factors:
(only use as.factor on categorical data)

```{r}
ratings$rating <- as.factor(ratings$rating)
levels(ratings$rating)
```




```{r}
ratings$artist_song <- as.factor(ratings$artist_song)
levels(ratings$artist_song)

ratings$pseudonym <- as.factor(ratings$pseudonym)
favorite_song$pseudonym <- as.factor(favorite_song$pseudonym)
levels(favorite_song$pseudonym)
levels(ratings$pseudonym)


#separate(ratings, artist_song, "song", sep = "([^\t]+)")

#left_join <- left_join(favorite_song, ratings, by = "pseudonym")
#right_join <- right_join(favorite_song, ratings, by = "pseudonym")
#full_join <- full_join(favorite_song, ratings, by = "pseudonym")
#inner_join <- inner_join(favorite_song, ratings, by = "pseudonym")

```

```{r}
talents <- tibble(pseudonym = survey$pseudonym, instruments = survey$instrument_list)
talents <- separate_rows(talents, -pseudonym, sep = ",")
talents$instruments <- talents$instruments %>%
                        trimws() %>%
                        tolower() %>%
                        str_replace_all(pattern = ".*piano.*", "piano") %>%
                        str_replace_all(patter = ".*ukulele.*", "ukulele") %>%
                        as.factor()
```



Visualizations:

```{r}
library("ggplot2")

ggplot(person, aes(year_born)) + geom_density()
ggplot(person, aes(year_born)) + geom_histogram(binwidth = 1)
ggplot(person, aes(year_born)) + geom_bar()
```

